HUME: Human UCCA-based Machine-Translation Evaluation

### 2016-03-07 paper/main.tex
zzz

In this work we propose the Human UCCA-based MT Evaluation ({\it HUME}) metric,
a human evaluation measure that decomposes over the sentence's semantic units.
The units are defined according to the 
UCCA scheme \cite{abend2013universal}, an appealing candidate for semantic analysis,
due to its cross-linguistic applicability, support for rapid annotation, and coverage
of many fundamental semantic phenomena, such as verbal, nominal and adjectival
argument structures and the inter-relations between them.
In contrast to previous proposals of semantic MT evaluation,

@@

@@

% MT evaluation
\paragraph{MT Evaluation.}

>>>>

In this work we propose the Human UCCA-based MT Evaluation ({\it HUME}) metric,
a human evaluation measure that decomposes over the sentence's semantic units.
The units are defined according to the 
UCCA scheme \cite{abend2013universal}, an appealing candidate for semantic analysis,
due to its cross-linguistic applicability, support for rapid annotation, and coverage
of many fundamental semantic phenomena, such as verbal, nominal and adjectival
argument structures and the inter-relations between them.

@@

While keeping a human in the loop is never a scalable solution, human evaluation is the
fundamental measure of quality of MT output, and we therefore begin our inquiries here.

@@

\paragraph{Machine Translation Evaluation.}
MT evaluation measures has been traditionally pursued through human-based
evaluation that quantifies the adequacy of the translation in preserving the meaning
of the source sentence, and its fluency as a sentence in the target language.
Human evaluation is still accepted as the standard evaluation measure, and is
estimated either in terms of the relative ranking of the outputs of multiple systems
(as is standard in the WMT shared tasks \cite[inter alia]{wmt14}, or by assigning
indiviaul adequacy/fluency scores for each sentence, recently streamlined by \newcite{graham2015}.
The problem with these measures is that they are costly to conduct on large scale, as
they require a human in the loop.

While providing the cleanest signal, human-based evaluation are not ideal for cases where
a wide variety of systems needs to be evaluated (e.g., with many different settings of hyper-parameters),
which has motivated the construction of cheaper methods that correlate with human
judgement. A common approach is to compare the MT output with reference translations,
created or verified by an expert. Methods often rely on some sort of string matching
methods, such as overlap of n-grams, as with the BLEU and METEOR measures, or edit
distance. While these measures greatly supported MT research by allowing to cheply
conduct many MT experiments, they suffer from two principal problems.
First, they rely on comparison to reference translations, which reflect a small
number out of the enormous number of ways to translate a sentence and are thus
inherently incomplete. Second, they decompose over the words and n-grams of the sentence,
and not over their lexical units, and are thus better suited for localizing errors
when evaluating shallow MT methods, and are less telling for identifying the semantic
nature of translation errors in the output.

To address the second issue, more structure-aware methods were proposed, with the
purpose of quantifying how different the reference and translation output are in terms
of their {\it structure}. \newcite{LiuGildea2005} took a syntactic approach, checking
syntactic similarity between the reference and translation\oa{verify!}. \newcite{Owczarzak2008}
took a similar approach using lexical-functional grammar structures.

Comparison of semantic structures with a reference translation
was conducted by \newcite{gimenezMarquez2007,gimenezMarquez2008},
who incorapoted them as features that were combined with lexical and morphosyntactic features.
Perhaps the most notable attempt at a semantic MT evaluation measure is MEANT \cite{lo2011meant} and
its human variant HMEANT, which compares the reference and translation in terms of their semantic
role labeling structure. The measure shares much of HUME's motivation for providing a measure that
decomposes over semantic units, rather than strings. Nevertheless, HMEANT suffers from several major
shortcomings, in that it is not able to capture much frequent phenomena that is not expressed
in the semantic structures, in addition to not addressing the problems incurred by using references.
HUME addresses both of these shortcomings, see \secref{sec:hmeant_comp}.
